Region-network hierarchical sparsity priors for\\ high-dimensional inference in brain imaging

### 2016-02-01 paper/paper.tex
started on optimization

@@

>>>>

One can read off the formula that decreasing \(\alpha\) leads to less 
penalization of brain networks and thus to tendentially fully active groups
and dense brain maps. If at the same time \(\beta\) is increased to a point
of inducing group sparsity, then only the structure of brain regions encoded
by \(\mathcal G\) is present. Conversely, if \(\beta\) is decreased to 
become non-selective, and \(\alpha\) is increased to group selectivity,
then the structure imposed will come from \(\mathcal H\), leading to the
selection of brain networks rather than regions.

It is important to note that the above trade-off shows that predominance
can be either attributed to regions or networks, but that nevertheless the
penalty structure is hierarchical: If the network penalty layer sets a
network group to zero, then all the contained region groups are forced to
have activity zero. Conversely, if a brain region has non-zero coefficients,
then necessarily the network containing it must be active.
This relation is asymmetric, since when swapping the roles of \(\mathcal G\)
 and \(\mathcal H\), these statements do not hold true anymore. A brain 
region can set all its coefficients to zero without forcing the 
corresponding network to zero. A brain network can be active without its
subregions necessarily being active.
When evaluating the trade-off in \((\alpha, \beta)\), this needs to be taken
into account.

@@

\paragraph{Optimization.}
We optimize the data loss function using an iterative forward-backward
scheme analogous to (F)ISTA for the lasso \cite{beck2009}. We divide the
loss \(\mathcal L(w)\) into a smooth, convex data fit term \(F(w)\) (here: 
logistic regression loss) and a potentially non-smooth, convex 
regularization term
